### 2013-09-24 phd/menger.tex
Updated filling results and todos

    However, we may show that $F\not\ktactwin{2}\sfillgame{J}$ | let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.

@@

>>>>

    By Prop 9 in Scheeper's paper, $F\not\ktactwin{2}\sfillgame{J}$ immediately. A proof follows: let $\sigma$ be a $2$-tactical strategy such that $\sigma(M)\subseteq\sigma(M,M')$.

@@

  \begin{theorem}
    $F\kmarkwin{k}\kfillgame{\kappa} \Rightarrow F\kmarkwin{k}\mengame{\oneptlind{\kappa}}$
  \end{theorem}

  \begin{proof}
    Assume $\sigma$ is a winning $k$-Mark\"ov strategy for $F\kmarkwin{k}\kfillgame{\kappa}$, where 
      \[
        \sigma(C_0,0)\subseteq
        \dots \subseteq
        \sigma(\mc C_0,\dots,\mc C_{k-2},k-2) \subseteq
        \sigma(C_0,C_1,\dots,C_{k-1},k-1)
      \]
    for all $n<\omega$.

    For each open cover $\mc U$ of $\oneptlind{\kappa}$, let $C(\mc U)$ be a countable set such that $\oneptlind{\kappa}\setminus C(\mc U)$ is in a refinement of $\mc U$. We define $\tau^*$ as follows:

      \[
        \tau^*(\mc U_0,0) =
        \oneptlind{\kappa}\setminus C(\mc U_0)
      \]
      \[
        \tau^*(\mc U_0,\mc U_1,1) =
        \dots =
        \tau^*(\mc U_0,\dots,\mc U_{k-2},k-2) =
        \emptyset
      \]
      \[
        \tau^*(\mc U_0,\dots,\mc U_{k-1},n+k-1) = 
        \sigma(C(\mc U_0),\dots,C(\mc U_{k-1}),n+k-1)
      \]

    If $\tau$ yields legal open sets covering $\tau^*$, then we claim $\tau$ is a winning strategy. Note that for any attack $\mc U_0,\mc U_1,\dots$ that $\tau$ covers $\oneptlind{\kappa}\setminus C(\mc U_0)$ in the initial round, and also covers
      \[
        \bigcup_{n<\omega}\sigma(C(\mc U_n),\dots,C(\mc U_{n+k-1}),n+k-1) \supseteq
        \bigcup_{n<\omega} C(\mc U_n) \supseteq
        C(\mc U_0)
      \]
    by the game's end.
  \end{proof}
